Project assignment - Tahoe-LAFS with SHA-3 candidates

### 2010-12-14 paper/main.tex
Removed some eol whitespace

\paragraph{Extra compiler flags}
%TODO: Vi har andre compiler argumenter - dette må diskuteres
We do not compile the candidate implementation with the exact same arguments
that is used in \ac{SUPERCOP}, most notably we append the -fPIC flag. This flag
creates position-independant-code, in other words machine instruction code that
can execute properly regardless of where in memory it resides. This will make
one less register available on the x86 architecture. While we cannot directly
prove that this will affect performance of the implementations. We do however
suspect it. A person writing an optimization for \ac{SUPERCOP} will have to
balance his use of resources, among them registers, to achieve maximum speed.
The loss of one register will then give a performance penalty.

@@

\subsection{Small files}
For small files, 1B and 1KB, we can clearly see that both double \ac{SHA}-256 
greatly outperforms the \ac{SHA}-3 candidate implementations. The data being 
hashed for these files are dominated by lengths of 63 and 106 bytes. By 
comparing with \ac{SUPERCOP} results, and especially the fact that we are 
using double \ac{SHA}-256, which should result in large overhead this is
unexpected. However, we believe that the results for small files may also
reflect our use of Cython and our skill. Given large amounts of call to our
bindings, while the data processed by the actual hash functions is small and
therefore does not use a lot of time, the speed of the bindings will come in to
play.

@@

%FIXME: Nevn noe en plass om at vi kanskje burde timet kallene til HASH
%funksjonen også.
\subsection{Impact of double \ac{SHA}-256}
The impact of using double \ac{SHA}-256 compared to single is suprisingly
small, even if you use the best-case estimate from Table
\ref{tbl:supercop:sha256}. For 1B, 1KB and 1MB files the data hashed is almost
exclusively 106B or less. If we assume data is hashed at the performance of 576
bytes, single \ac{SHA}-256 should outperform double \ac{SHA}-256 by about 10\%.
For 1B files this difference is eaten up by external factors (other
processes), the same goes for 1KB files. For 1MB files, there seems to be a
difference, however this difference is so small that we deem it unimportant.
For the larger files the performance penalty is even smaller, so all in all we
deem the performance penalty for Tahoe-\ac{LAFS} for using double \ac{SHA}-256
as opposed to single unimportant.

@@

\section{Improvement of methods}
% More general stuff. What could have been done differently? Criticize
% ourselves.
%
% Optimized candidates - which gain could be expected from more optimized
%   candidates?

@@

>>>>

\paragraph{Extra compiler flags}

We do not compile the candidate implementation with the exact same arguments
that is used in \ac{SUPERCOP}, most notably we append the -fPIC flag. This flag
creates \emph{position independent code}, in other words machine instruction
code that can execute properly regardless of where in memory it resides. This
will make one less register available on the x86 architecture. While we cannot
directly prove that this will affect performance of the implementations. We do
however suspect it. A person writing an optimization for \ac{SUPERCOP} will have
to balance his use of resources, among them registers, to achieve maximum speed.
The loss of one register will then give a performance penalty.

@@

\subsection{Small files}

For small files, 1B and 1KB, we can clearly see that both double \ac{SHA}-256
greatly outperforms the \ac{SHA}-3 candidate implementations. The data being
hashed for these files are dominated by lengths of 63 and 106 bytes. By
comparing with \ac{SUPERCOP} results, and especially the fact that we are using
double \ac{SHA}-256, which should result in large overhead this is unexpected.
However, we believe that the results for small files may also reflect our use of
Cython and our skill. Given large amounts of call to our bindings, while the
data processed by the actual hash functions is small and therefore does not use
a lot of time, the speed of the bindings will come in to play.

@@

\subsection{Impact of double \ac{SHA}-256}
The impact of using double \ac{SHA}-256 compared to single is surprisingly
small, even if you use the best-case estimate from Table
\ref{tbl:supercop:sha256}. For 1B, 1KB and 1MB files the data hashed is almost
exclusively 106B or less. If we assume data is hashed at the performance of 576
bytes, single \ac{SHA}-256 should outperform double \ac{SHA}-256 by about 10\%.
For 1B files this difference is eaten up by external factors (other
processes), the same goes for 1KB files. For 1MB files, there seems to be a
difference, however this difference is so small that we deem it unimportant.
For the larger files the performance penalty is even smaller, so all in all we
deem the performance penalty for Tahoe-\ac{LAFS} for using double \ac{SHA}-256
as opposed to single unimportant.

@@

\section{Improvement of methods}

@@

% TODO: Discuss the BLAKE run in Results when timing was done within Cython.
